---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

# Global Pedons

[![Binder](https://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jjmaynard/Global.Pedons/master?urlpath=rstudio)

This repository contains the data and code for the LandPKS Global Soil Pedon Database.

Project Website:
https://jjmaynard.github.io/Global.Pedons/



```{r gh-installation, eval = FALSE}
# install.packages("devtools")
remotes::install_github("jjmaynard/Global.Pedons")
```


### Licenses

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code :** See the [DESCRIPTION](DESCRIPTION) file

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

