---
title: "Mexico Pedon Processing"
output: html_notebook
---

```{r, echo=FALSE}
required.packages <- c("here", "gdalUtils", "rgdal", "RODBC", "GSIF", "xlsx", "sf", "tidyverse", "viridis", "rvest", "foreign", "dplyr", "aqp", "soilDB", "colorspace", "stringr", "cluster", "sharpshootR", "colorscience", "reshape2", "purrr", "jsonlite", "hexbin", "rms", "farver", "openxlsx")
new.packages <- required.packages[!(required.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)
lapply(required.packages, require, character.only=T)
rm(required.packages, new.packages)

setwd("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico")
data(soil.classes)
```

# Load in the two pedon databases for Mexico

  1. Mexico Pedon dataset #1 (perfilv12) 1980-1996, 9,549 profiles
  2. Mexico Pedon dataset #2 (perfiles_serieii) 1998-2007, 2,940 profiles 
```{r}
mexico_pedon1 <- st_read("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico/Soil_Profiles_SerieI/shape/perfilv12.shp", quiet = TRUE)

mexico_pedon2 <- st_read("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico/Soil_Profiles_SerieII/perfiles_suelos_shp/perfiles_serieii.shp", quiet = TRUE)

# Define projections and reproject
st_crs(mexico_pedon2) <- 6362 # EPSG:6362 Mexico ITRF92 / LCC

mexico_pedon1 <- st_transform(mexico_pedon1, 4326)
mexico_pedon2 <- st_transform(mexico_pedon2, 4326)

# Number of unique pedons
points <- c(st_geometry(mexico_pedon2), st_geometry(mexico_pedon1))
length(unique(points)) # 13,964 pedons

```

# Processing of Mexico Pedon dataset #1 (perfilv12)
## Step 1: Subset and rename data columns
```{r}
mexico_pedon1_sub <- mexico_pedon1  %>% dplyr::mutate(FAO="FAO68") %>% dplyr::mutate(Lim=ifelse(LIM_ROCA=="x", "BedR", ifelse(LIM_REGO=="x", "Rego", ifelse(LIM_CEME=="x", "Cem", ifelse(LIM_NIVF=="x", "Wat", NA))))) %>% dplyr::select(ID=IDENTIFI, FAO, FAO_Code=FAO68, Lim, A_ColorD=A_COLORS, A_ColorM=A_COLORH, E_ColorD=E_COLOR, B_ColorM=B_COLORH, HONU=NHORIZON, HzName=HSIMBOLO, TOPDEP=HLIMSUPE, BOTDEP=HLIMINFE, Clay=ARCILLA, Silt=LIMO, Sand=ARENA, ColorD = COLORSEC, ColorM = COLORHUM,  ORGC=MO, geometry)

mexico_pedon1_sub <- mexico_pedon1_sub %>% group_by(ID) %>% filter(!all(is.na(TOPDEP)) & !all(is.na(BOTDEP))) %>% filter(HONU!=0) %>% ungroup()
mexico_pedon1_sub_coords <- do.call(rbind, st_geometry(mexico_pedon1_sub)) %>% as.data.frame() %>% setNames(c("lon","lat"))
st_geometry(mexico_pedon1_sub) <- NULL
mexico_pedon1_sub <- cbind(mexico_pedon1_sub, mexico_pedon1_sub_coords)
mexico_pedon1_sub <- mexico_pedon1_sub %>% dplyr::select(ID, FAO, FAO_Code, HONU, HzName, TOPDEP, BOTDEP, Clay, Silt, Sand, ColorD, ColorM, ORGC, lat, lon)

```

## Step 2: Taxonomy translation/harmonization.
Mexico Pedon dataset #1 used FAO68 taxonomy and is in spanish. Need to perform the following steps to translate and convert the taxonomy to FAO90
  1. Create FAO68 (assuming the same as FAO74) translation table
  2. Create conversion table between FA68 taxonomy names and FAO90 taxonomy names using the GSIF 'soil.classes' subtables and WRB documents
```{r}
FAO68 <-  read.csv("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico/Soil_Profiles_SerieI/FAO68_taxonomy_revised.csv", header=T)
names(FAO68) <- c("Code", "WRB_Taxo")
FAO68$WRB_Taxo <-  str_to_title(FAO68$WRB_Taxo)
mexico_pedon1_sub <- mexico_pedon1_sub %>% left_join(FAO68, by=c("FAO_Code"="Code"))

# 347 pedons had FAO taxonomy codes that did not exist. I have excluded these
mexico_pedon1_sub <- mexico_pedon1_sub %>% filter(!is.na(WRB_Taxo)) # 4,286 pedons after filtering out pedons with no depth data


#Load in WRB translation tables
FAO74_WRB1994_LT <- soil.classes$WRB_versions %>% select(World_Soil_Map_1974_Group, World_Soil_Map_1974_Subgroup, WRB_1994_Group, WRB_1994_Subgroup, FAO_1974_NAME, WRB_1994_NAME) %>% distinct()






WRB_RSG_2006 <- read.xlsx("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico/WRB_Reference_Soil_Groups_2006.xlsx")
names(WRB_RSG_2006) <- c("RSG_name_en", "RSG_name_sp", "RSG_code")
WRB_Qual_2006 <- read.xlsx("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico/WRB_qualifiers_specifiers_2006.xlsx")
names(WRB_Qual_2006) <- c("Qual_name_en", "Qual_name_sp", "Qual_code")

LPKS_WRB_FAO90_Tax <- read.csv("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico/LPKS_WRB_FAO90_Tax.csv", header=T)
WRB_Qual_2006[which(!WRB_Qual_2006$Qual_name_en %in% LPKS_WRB_FAO90_Tax$Qual),]
WRB_Qual_2006[which(!WRB_Qual_2006$Qual_name_en %in% LPKS_WRB_FAO90_Tax$Qual),]
# Used code to manually edit xlsx lookup table
# WRB_Qual_2006_missing <- read.xlsx("C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/Mexico/WRB_qualifiers_specifiers_2006_missing.xlsx")
# names(WRB_Qual_2006_missing) <- c("Qual_name_sp1", "Qual_name_sp2")
# WRB_Qual_2006_missing <- WRB_Qual_2006_missing %>% mutate(Qual_name_sp2 = str_to_title(Qual_name_sp2))
# WRB_Qual_2006_missing <- WRB_Qual_2006_missing %>% left_join(WRB_Qual_2006, by=c("Qual_name_sp2"="Qual_name_sp"))




```


# Processing of Mexico Pedon dataset #2 (perfiles_serieii)
```{r}
pedon2_wrb <- mexico_pedon2  %>% dplyr::select(GPO_SUELO,  CALIF_PRIM, CALIF_SEC)
st_geometry(pedon2_wrb) <- NULL
pedon2_wrb <- pedon2_wrb %>% mutate(CALIF_PRIM=as.character(CALIF_PRIM))
pedon2_wrb <- pedon2_wrb %>% mutate(CALIF_PRIM=ifelse(CALIF_PRIM == "Síltico", "Límico", CALIF_PRIM))
pedon2_wrb <- pedon2_wrb %>% mutate(GPO_SUELO = str_to_title(GPO_SUELO))
pedon2_wrb <- pedon2_wrb %>% left_join(WRB_RSG_2006, by=c("GPO_SUELO"="RSG_name_sp")) 
pedon2_wrb <- pedon2_wrb %>% left_join(WRB_Qual_2006, by=c("CALIF_PRIM"="Qual_name_sp"))
 
pedon2_wrb <- pedon2_wrb %>% mutate(WRB_2006 = str_c(Qual_name_en, RSG_name_en, sep=" "))

LPKS_WRB_FAO90_Tax$WRB_tax <- str_sub(LPKS_WRB_FAO90_Tax$WRB_tax, start = 1, end = -2)

missing <- pedon2_wrb[which(!pedon2_wrb$WRB_2006 %in% LPKS_WRB_FAO90_Tax$WRB_tax),]


mexico_pedon2$WRB_2006 <- pedon2_wrb$WRB_2006

pedon2_id <- str_split_fixed(mexico_pedon2$ID_PERFIL, "-", 2)
mexico_pedon2_sub <- mexico_pedon2  %>% dplyr::mutate(FAO="FAO90?", HONU=as.numeric(pedon2_id[,2]), ID=as.numeric(pedon2_id[,1])) %>% dplyr::select(ID, FAO, FAO_Code=CLAVE_WRB, HONU, HzName=NOMEN_HTE, TOPDEP=LIM_SUP, BOTDEP=LIM_INF, Clay=R, Silt=L, Sand=A, rf=F_RúDICA, ColorD = COL_SECO_L, ColorM = COL_HUM_L, Color_FieldM=COL_CAMPO, ORGC=CO, WRB_2006, geometry)






mexico_pedons <- mexico_pedon1_sub  %>% dplyr::select(ID, FAO, FAO_Code, HONU, HzName, TOPDEP, BOTDEP, Clay, Silt, Sand, ColorD, ColorM,  ORGC, geometry)

```

