---
title: "KSSL + NASIS Data Processing (Updated)"
output: html_notebook
---



### This script processes the KSSL NCSS SCD and NASIS pedon data to create a combined pedon database with both morphology and soil chemical data. The code uses the newest KSSL and NASIS data found on the NRCS cloudVault (https://new.cloudvault.usda.gov/index.php/s/eSoPYbWDBQNX2HP). Some code from Dylan Beaudette's KSSL processing steps were used as described here: (https://github.com/dylanbeaudette/process-kssl-snapshot).Details of the new snapshot datasets are described in the NCSS-Tech workgroup notes from 2019-03-12 (https://github.com/ncss-tech/lab-data-delivery/blob/master/meeting-notes/meeting-notes-2019-03-12.md)
```{r}
library(soilDB)
library(aqp)
library(stringi)
library(rvest)
library(dplyr)
library(tidyr)
library(tibble)
library(lubridate)
library(stringr)
library(tidyverse)
library(sf)
library(colorspace)

```


##Load in data tables from NCSS SCD
```{r}
KSSL_layers_new <- st_layers(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Tech_Data_Download/KSSL_Download_20200114/NCSS_Characterization_Database_newSchema_20200114.gdb")

# Driver: OpenFileGDB 
# Available layers:
#                                                 layer_name geometry_type features fields
# 1                                       combine_nasis_ncss         Point    65949     80
# 2                                                    pedon            NA    65966     10
# 3                                              preparation            NA       62      8
# 4                                                  rosetta            NA    79326     11
# 5                                   lab_analysis_procedure            NA      514     10
# 6  lab_calculations_including_estimates_and_default_values            NA   299483     81
# 7                                  lab_chemical_properties            NA   319086    207
# 8                  lab_major_and_trace_elements_and_oxides            NA    32694     42
# 9                                          lab_method_code            NA      806      9
# 10                              lab_mineralogy_glass_count            NA    34944    195
# 11                                 lab_physical_properties            NA   886111    120
# 12                                    lab_xray_and_thermal            NA    66584    100
# 13                                                    site            NA   128240     14
# 14                                              lab_webmap            NA    53603     16
# 15                                                   layer            NA   410011     22
# 16                                                 analyte            NA      530      5
# 17                                                lab_area            NA    12011      9

combine_nasis_ncss  <- st_read(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Tech_Data_Download/KSSL_Download_20200114/NCSS_Characterization_Database_newSchema_20200114.gdb", layer=KSSL_layers_new[[1]][1]) 

#many more sites than pedons or data. it looks like this table isn't needed since we can just use the 'combine_nasis_ncss'
# ncss_site_new  <- st_read(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Tech_Data_Download/KSSL_Download_20200114/NCSS_Characterization_Database_newSchema_20200114.gdb", layer=KSSL_layers_new[[1]][13]) 

#here is the bulk of the data to join
ncss_chem  <- st_read(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Tech_Data_Download/KSSL_Download_20200114/NCSS_Characterization_Database_newSchema_20200114.gdb", layer=KSSL_layers_new[[1]][7]) 
ncss_phys  <- st_read(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Tech_Data_Download/KSSL_Download_20200114/NCSS_Characterization_Database_newSchema_20200114.gdb", layer=KSSL_layers_new[[1]][11]) 
ncss_layer  <- st_read(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Tech_Data_Download/KSSL_Download_20200114/NCSS_Characterization_Database_newSchema_20200114.gdb", layer=KSSL_layers_new[[1]][15]) 

NCSS_hz_new <- combine_nasis_ncss %>% 
              left_join(ncss_chem, by = c("pedlabsampnum"="labsampnum"))  %>% 
              left_join(ncss_phys, by = c("pedlabsampnum"="labsampnum"))  %>% 
              dplyr::select(pedon_key, site_key, layer_key, pedlabsampnum, layer_sequence, hzn_top, hzn_bot, hzn_desgn, hzn_desgn_old, texture_lab , sand_total, silt_total, clay_total, total_frag_wt_pct_gt_2_mm_ws, total_carbon_ncs, organic_carbon_walkley_black, estimated_organic_carbon, horizontal_datum_name, latitude_direction, latitude_degrees, latitude_minutes, latitude_seconds, longitude_direction, longitude_degrees, longitude_minutes, longitude_seconds, latitude_std_decimal_degrees, longitude_std_decimal_degrees) %>%
              rename(lab_texture_class = texture_lab , sand = sand_total, silt = silt_total, clay = clay_total, frags_tot = total_frag_wt_pct_gt_2_mm_ws, toc = total_carbon_ncs, oc = organic_carbon_walkley_black, oc_est = estimated_organic_carbon)  %>%
              distinct()  %>% 
              arrange(pedon_key, hzn_top)  %>% 
              filter(!is.na(labsampnum))


NCSS_hz_new %>% filter(!is.na(latitude_std_decimal_degrees)) %>% select(pedon_key) %>% distinct() %>% pull() %>% length()


KSSL_layers <- st_layers(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Soil_Characterization_Database/NCSS_Soil_Characterization_Database_09_14_2018.gdb")


NCSS_hz_new <- ncss_site_new %>% 
              left_join(ncss_layer, by = "site_key")
```

```{r}
#More recent NASIS data from 2020 snapshot
NASIS_layers <- st_layers(dsn="C:/R_Drive/Data_Files/ARS_Data/Research_Projects/LandPKS/Soil_Pedon_Databases/KSSL/NCSS_Tech_Data_Download/KSSL_Download_20200114/NASIS_Morphological_20200116.gdb")

# Driver: OpenFileGDB 
# Available layers:
#                         layer_name geometry_type features fields
# 1              MetadataCardinality            NA        4      2
# 2             MetadataColumnLookup            NA     2673     11
# 3              MetadataIndexDetail            NA     1920      5
# 4       MetadataRelationshipDetail            NA      981     11
# 5       MetadataRelationshipMaster            NA      914     15
# 6                    MetadataTable            NA      454     16
# 7                 ncsslayerlabdata            NA   359783     84
# 8                 ncsspedonlabdata            NA   359783     20
# 9                   pediagfeatures            NA    59265     11
# 10           pedondbcolumnmetadata            NA     1018      5
# 11            pedondbtablemetadata            NA       71      5
# 12                           pefmp            NA     6948      8
# 13          pehydricfieldindicator            NA      391      6
# 14                peinfiltrationch            NA        8     13
# 15            peinfiltrationchdata            NA        0      9
# 16                peinfiltrationfh            NA       75     11
# 17            peinfiltrationfhdata            NA        2      7
# 18           peinfiltrationsummary            NA      116     10
# 19         pepenetrationresistance            NA      306     15
# 20                  perestrictions            NA     3996     12
# 21                 pesoilstability            NA      307     16
# 22                  petaxhistfmmin            NA    58971      7
# 23                petaxhistmoistcl            NA    41111      6
# 24                    petaxhistory            NA    86939     30
# 25                          petext            NA    33476     11
# 26                 petxhistfmother            NA    15719      6
# 27                      phcemagent            NA      863      6
# 28                      phcoledata            NA        0      8
# 29                         phcolor            NA   517056     11
# 30                     phconccolor            NA     7944     10
# 31                         phconcs            NA    39104     13
# 32                        phcracks            NA      167     11
# 33                            phdb            NA      696     29
# 34             phdbcompliantcavity            NA        1     15
# 35                        phdbcore            NA      465     12
# 36                 phdbcorereading            NA       40      5
# 37                       phdbscoop            NA       77     13
# 38                phdbscoopreading            NA       36      5
# 39                   phdesgnsuffix            NA   193845      6
# 40                     phfeatcolor            NA      654     10
# 41                      phfeatures            NA     2817     12
# 42                           phfmp            NA     4987      8
# 43                         phfrags            NA   161243     15
# 44                   phgrcountdata            NA        0     13
# 45                phgrcountsummary            NA       10     11
# 46                        phhuarts            NA      534     16
# 47            phhydrometeranalysis            NA       14     11
# 48                phhydrometerdata            NA       32      8
# 49                phksatamoozedata            NA        0     10
# 50               phksatamoozemeter            NA       14     14
# 51                      phksatring            NA        0     16
# 52                  phksatringdata            NA        0      9
# 53                   phksatsummary            NA      119     10
# 54                    phlabresults            NA    15450     62
# 55                       phmottles            NA    61750     14
# 56                        phorizon            NA   425589     69
# 57                         phpores            NA   145538     10
# 58                          phpvsf            NA   166817     10
# 59                     phpvsfcolor            NA   102402     10
# 60                   phrdxfeatures            NA   127348     13
# 61                   phredoxfcolor            NA   105125     10
# 62                         phroots            NA   269770      9
# 63                        phsample            NA   393105     13
# 64                     phstructure            NA   412786     10
# 65                          phtext            NA   168873     11
# 66                       phtexture            NA   365208      7
# 67                    phtexturemod            NA    59676      6
# 68                      phvnirscan            NA        0     10
# 69                phvnirscanresult            NA        0     10
# 70                 plotdisturbance            NA        0     10
# 71                  plotgrazinguse            NA        0      9
# 72      plotmainforeststanddetails            NA        0     11
# 73              plotplantinventory            NA        0     32
# 74        plotplanttypecanopycover            NA        0     11
# 75        plotsamplingprotocolused            NA        0      9
# 76            plotspeciesbasalarea            NA        0      9
# 77               plottreeinventory            NA        0     10
# 78                plottreescounted            NA        0      7
# 79        plottreesiteindexdetails            NA        0     17
# 80        plottreesiteindexsummary            NA        0     13
# 81                 plottreesummary            NA        0      9
# 82                    siteaoverlap            NA   109679      7
# 83                     sitebedrock            NA    12383     15
# 84                    siteassocsoi            NA    12729      4
# 85              siteecositehistory            NA      675      5
# 86                   siteassocsite            NA        0      4
# 87                  sitegeomordesc            NA    58896      7
# 88                         siteobs            NA    64817     50
# 89                          sitepm            NA    58846     11
# 90                        sitetext            NA     6804      9
# 91                       siteassoc            NA        0      3
# 92                  siteerosionacc            NA    14193      4
# 93                     siteobstext            NA     2714      9
# 94                   sitesoilmoist            NA     6142     11
# 95                    sitesoiltemp            NA     1093      6
# 96                   sitesurffrags            NA     7977     12
# 97                   siteassoctext            NA        0      9
# 98                        transect            NA     2772      9
# 99          transectestcomposition            NA       94      8
# 100                   transecttext            NA      221      9
# 101                       beltdata            NA        0      9
# 102      daubenmirecancovclasssumm            NA        0      9
# 103     daubenmirecancovquaddetail            NA        0      6
# 104          densityquadratdetails            NA        0     11
# 105              dwrquadratdetails            NA        0     10
# 106        frequencyquadratdetails            NA        0      8
# 107       nestedfreqquadratdetails            NA        0      8
# 108         nestedfrequencysummary            NA        0      9
# 109               windbreakrowdata            NA        0     39
# 110           comparativeyielddata            NA        0      8
# 111    comparativeyieldrefquadrats            NA        0     10
# 112                croptreedetails            NA        0     11
# 113         croptreesubplotdetails            NA        0      9
# 114                croptreesummary            NA        0     14
# 115                 croptreetotals            NA        0      9
# 116               groundcovdetails            NA        0      8
# 117           groundsurfcovdetails            NA        0      8
# 118        plantprodquadratdetails            NA        0     15
# 119               siteiristubedata            NA       16     12
# 120                  sitemuoverlap            NA    12574      6
# 121                siteothvegclass            NA      189      6
# 122               sitetreescounted            NA        0      7
# 123      siteusgsquadrangleoverlap            NA        0      6
# 124             sitewoodybasalarea            NA        0      7
# 125           soilmoistmonitordata            NA        2     11
# 126                soilmonitordata            NA        3     12
# 127            soiltempmonitordata            NA        1     11
# 128            subplotplantdetails            NA        0      9
# 129            totalquadratharvest            NA        0      8
# 130             transectgapdetails            NA        0     10
# 131            transectgroundcover            NA        0     11
# 132  transectgroundcoverdatalegacy            NA        0     10
# 133        transectgroundsurfcover            NA        0     11
# 134   transectoverstorycanopycover            NA        0     10
# 135   transectsamplingprotocolused            NA        0      9
# 136 transectstandingbiomassdetails            NA        0     11
# 137                    vegplottext            NA        0     11
# 138                    vegtransect            NA        0     70
# 139        vegtransectplantsummary            NA        0     78
# 140                vegtransecttext            NA        0     11
# 141          basalareatreescounted            NA        0      8
# 142            belttransectsummary            NA        0      9
# 143         pointplantcoverdetails            NA        0     11
# 144                        vegplot            NA        0    168
# 145                           area            NA        0      7
# 146                 ecologicalsite            NA        0      7
# 147                       areatype            NA        0      4
# 148           MetadataDomainDetail            NA     6830      8
# 149                          pedon         Point    64817     67
# 150                           site            NA    64817     69


```




